### 2023-08-23 project_Luis_PhD/paper.tex
updated

\def\Student{Ashish Sehrawat}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}

@@

%%%%Title Page
\begin{titlepage}
\centering
\hspace{0pt}
\vfill
{\scshape\Large \Title \par}
project revised 2021-1

@@

  This research project proposes to determine precise value and corresponding uncertainity of luminosity delivered to Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period using Pixel Cluster Counting (PCC) method and construction of luminosity measurement device using Tracker Endcap Pixel Detector (TEPX) for High Luminosity (HL)-LHC which will be able to withstand luminosities of up to 3000 $fb^{-1}$. Luminosity plays a vital role in determination of cross section for various production and decay processes of elementary particles and its accurate determination will assist in precise calculation of SM quantities like cross section, couplings and exploring physics beyond SM.

@@

This project has two main parts, in the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.
In the second part we develop an upgraded luminosity measurement system for the HL-LHC phase (2026-2038).

@@

The main objective of this work is to perform a measurement of the 2017-2018 LHC delivered luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
This precision is necesary for testing SM of elementary particles and identifying possible new physics which could elucidate the nature of Dark Matter in our universe.

The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX). TEPX is a part of new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).

@@

As mentioned in the introduction, precision achieved in the measurement of integrated luminosity during Run 1 was about 2.5\% using  methods developed for the first time.
In 2015 and 2016 the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt}.
The methods used for the 2015 and 2016 data are similar to the strategy we propose in this project.
We expect that the final uncertainties for the 2017 and 2018 datasets to be similar, but the ultimate goal of the CMS collaboration is to reduce these uncertainties to below 1\%  \cite{Dainese:2019rgk}.

For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components. 
However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.

@@

\item {\bf Semester 1 (2019-2)}:
  \SubItem{ Readings on Standard Model of particle physics theory}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Initial planning of the analysis strategy}

\item {\bf Semester 2 (2020-1)}:
  \SubItem{ Course I on particle physics, particle detection, or data analysis}
  \SubItem{ Readings on the LHC and CMS experiments}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Computing accounts at CERN and Fermilab}
  \SubItem{ Studies of the TEPX luminometer upgrade}

\item {\bf Semester 3 (2020-2)}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
  \SubItem{ Studies of the TEPX luminometer upgrade}

\item {\bf Semester 4 (2021-1)}:
  \SubItem{ Completion of the TEPX luminometer studies for the TDR document}
  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
  \SubItem{ Writing of the monograph}

\item {\bf Semester 5 (2021-2)}:
  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC for review}
  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
  \SubItem{ Studies of the LHC Run 2 data using the PCC method}

\item {\bf Semester 6 (2022-1)}:
  \SubItem{ Completion of the studies of the Run 2 data luminosity measurement}
  \SubItem{ Writing of the Run 2 data luminosity measurement publication and review within the CMS collaboration}

\item {\bf Semester 7 (2022-2)}:
  \SubItem{ Publication of the Run 2 data luminosity measurement in a peer reviewed journal}

\item {\bf Semester 8 (2023-1)}: 
  \SubItem{ Presentations at national or international conferences for both the Run 2 luminosity measurement and TEPX luminometer for HL-LHC}
  \SubItem{ Writing of the Ph.D thesis}

>>>>

\def\Student{Luis Enrique Cuevas  Picos}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
\def\ResearchLine{F\'{i}sica de Part\'{i}culas}

@@

%%%%Title Page
\begin{titlepage}
\centering
\hspace{0pt}
\vfill
{\scshape\Large \Title \par}
project revised 2023-2

@@

  This research project proposes...

@@

This project propose...

@@

The main objective of this work is to perform...

@@

As mentioned in the introduction...

@@

\item {\bf Semester 1 (2023-2)}:
  \SubItem{ Readings on Standard Model of particle physics theory}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Initial planning of the analysis strategy}

\item {\bf Semester 2 (2024-1)}:
  \SubItem{ Course I on particle physics, particle detection, or data analysis}
  \SubItem{ Readings on the LHC and CMS experiments}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Computing accounts at CERN and Fermilab}
  \SubItem{ Studies of the TEPX luminometer upgrade}

\item {\bf Semester 3 (2024-2)}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
  \SubItem{ Studies of the TEPX luminometer upgrade}

\item {\bf Semester 4 (2025-1)}:
  \SubItem{ Completion of the TEPX luminometer studies for the TDR document}
  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
  \SubItem{ Writing of the monograph}

\item {\bf Semester 5 (2025-2)}:
  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC for review}
  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
  \SubItem{ Studies of the LHC Run 2 data using the PCC method}

\item {\bf Semester 6 (2026-1)}:
  \SubItem{ Completion of the studies of the Run 2 data luminosity measurement}
  \SubItem{ Writing of the Run 2 data luminosity measurement publication and review within the CMS collaboration}

\item {\bf Semester 7 (2026-2)}:
  \SubItem{ Publication of the Run 2 data luminosity measurement in a peer reviewed journal}

\item {\bf Semester 8 (2027-1)}: 
  \SubItem{ Presentations at national or international conferences for both the Run 2 luminosity measurement and TEPX luminometer for HL-LHC}
  \SubItem{ Writing of the Ph.D thesis}
